---
title: "formula_1"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
library(tidyverse)
library(knitr)
theme_set(theme_minimal())
```

## Summary of the data set

The following represents the dataset of the pit stops of formula 1 cars during races. It has 7 columns which are the raceid, driverid, stop, lap, time, duration and milliseconds.

```{r load data}
bc_data <- read_csv("data/pit_stops.csv")
bc_data 
```

## Plotting the lap number along with the lap time in millisconds

the following graph is a histogram of the lap number along with the time n milliseconds
```{r, include=TRUE}
hist_duration_lap <- bc_data |>
                                ggplot(aes(x = lap, fill =  milliseconds)) +
                                geom_histogram(bins = 20, color = 'white') 
# Show the plot at the end
hist_duration_lap
```
As we can see above, the histogram is skewed to the right. This suggest that , as the number of laps increases, the stop time at the pit reduces.

```{r, include=TRUE}

```


## Plotting the stop number along with the lap time in millisconds

the following graph is a bar plot of the stop number along with the stop time

```{r fig.width=9, fig.height=9}


hist_duration_stop <- bc_data |>
                                ggplot(aes(x = stop, fill =  milliseconds)) +
                                geom_histogram(bins = 20, color = 'white') +
                                xlab("Stop number") + 
                                ylab("Time in milliseconds")
# Show the plot at the end
hist_duration_stop
                        
```

In the graph above, we can observe that the early stops takes more time than the stops that happen later during the race.